Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-03 manuscript/manuscript.Rmd
Added combined plot.

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")
plot_theme$legend.key.size <- grid::unit(0.3, 'lines')

>>>>

# Set general theme.
plot_theme <- ggplot2::theme_light(base_size=base_size)
plot_theme$plot.title$size <- ggplot2::rel(1.0)
plot_theme$plot.title$hjust <- 0.5
plot_theme$strip.background <- ggplot2::element_blank()
plot_theme$strip.text$colour <- NULL
plot_theme$plot.margin <- grid::unit(c(2, 2, 2, 2), "points")
plot_theme$legend.key.size <- grid::unit(0.3, 'lines')
plot_theme$plot.tag <- ggplot2::element_text(
  size = ggplot2::rel(1.0),
  hjust = 0.0,
  vjust = 0.0,
  inherit.blank = FALSE
)
plot_theme$plot.tag.position <- c(0, 1)
